---
title: "HydroVuR - Example 1"
author: "Jaak Van den Sype"
date: "2022-04-07"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{HydroVuR-Example1}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(HydroVuR)
#devtools::load_all()
```

# Introduction

The following is a basic example of how to use the `HydroVuR` package to access the In-Situ HydroVu API.  Documentation of the API endpoint can be found at:  https://www.hydrovu.com/public-api/docs/index.html


# Authentication

To authenticate provide your client_id and key and get a token using `hv_auth()`.  The API credentials are managed on HydroVu site under Users | Manage API Access Credentials

```{r}

# set client id and key
client_id <- 'PublicApiDemo'
key <- 'PublicApiSecret'

# get a token
token <- hv_auth(client_id, key)

```

# Locations

Get a list of locations available for this access token using `hv_locations()`

```{r}

# get the locations
locs <- hv_locations(token)

knitr::kable(locs)

```

# Get Data

## Single Location

To get data from a location, supply the location name, start/end dates and the desired timezone to `hv_data()`.

Note: the timezone supplied is for **both** the input start/end times and the return data.


```{r}

vulink <- hv_data("In-Situ Poudre Well", "2000-01-01 00:00:00", Sys.time(), 
                tz = "America/New_York", token)

knitr::kable(vulink)

```

The data returned will e a `data.frame` in a "long" format which makes further analysis or plotting easier

```{r fig.height=4, fig.width=6}
library(ggplot2)

ggplot(vulink, aes(x = timestamp, y = value)) + 
  geom_point() + geom_line() + 
  facet_wrap(~Parameter, scales = 'free', ncol = 2)
```

## Multiple Locations

To get data from multiple locations at once, map over `hv_data()` and a vector of locations (for example, as returned from `hv_locations()`)

```{r}
library(purrr)

all_data <- purrr::map_dfr(locs$name, hv_data, 
                           start_time = "2000-01-01 00:00:00", end_time = Sys.time(),
                    tz = "America/New_York", token = token)

```

```{r fig.height=4, fig.width=6}

ggplot(all_data, aes(x = timestamp, y = value)) + 
  geom_point() + geom_line() + 
  facet_grid(Parameter ~ Location, scales = 'free')

```

# Other

A list of friendly name mappings for parameters and units can be accessed using the `hv_names()` function.  Note that `hv_data()` will already include the friendly names in the output by calling this function so generally there is no need to call this function directly.

`hv_names()` provides a `return` flag to control what is returned.  If `return = "params"` is set, a `data.frame` of the parameters is returned.  If `return = "units"` is set, a `data.frame` of unit names is returned, if no return is set, it defaults to `return = "both"` and a `list` containing the above two dataframes is returned.

```{r}
# get the Friendly Names
params <- hv_names(token, return = "params")

knitr::kable(head(params))
```

```{r}
units <- hv_names(token, return = "units")

knitr::kable(head(units))
```

```{r}
both <- hv_names(token)
print(both)
```

